Draft

### 2022-07-21 ms.tex
version 0721; caption of fig:tau added

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{tau.png}
\caption{
Left panel: BHMF at $z=$ 6 calculated with $\tlife= $. The solid lines denote modeled BHMF produced by the best-fit parameters 
and the shaded regions are the one sigma spread. 
Right panel: the mass density of BHs with $\Mbh > 10^7~\Msun$, integrated from the BHMF in the left panel.
}
\label{fig:tau}
\end{figure*}

>>>>

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{tau.png}
\caption{
Left panel: BHMF at $z=$ 6 calculated in the $\fseed=0.01$ case, 
with different $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively, 
and other parameters are fixed to the best-fit values. 
The blue curve denotes the BHMF constrained by the \citetalias{2010AJ....140..546W} result. 
With lower(higher) $\tlife$ than the best-fit value, the BHMF is under(over)-produced in the high mass end.
Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
With $\tlife$ values different from the best-fit value, the consequent QLF show 
similar trends of deviation from observation as in the BHMF curves.
}
\label{fig:tau}
\end{figure*}
